Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
More edits to introduction

## Arab Spring
In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
unjustifiably stripped of his vendor cart by municipal officials. His
humiliation led him to set himself on fire in protest to the authoritarian
rule, ultimately leading to his death several days later. His actions served
as a catalyst for the Tunisian Revolution, and one week after his death, the
long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the
country. The events of Tunisia rapidly spread to surrounding countries that
were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya,
and Syria. These mass movements would not have been possible without
efficient interpersonal coordination, both physically and virtually on social
media platforms, such as Twitter. The events of Arab Spring have been
thoroughly discussed within the political science literature
[e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge,
the use of Twitter by Syrian citizens has not been investigated.

>>>>

## Arab Spring
In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
unjustifiably stripped of his vendor cart by municipal officials. His
humiliation led him to set himself on fire in protest to the authoritarian
rule, ultimately leading to his death several days later. His actions served
as a catalyst for the Tunisian Revolution, and one week after his death,
Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
country. The events of Tunisia rapidly spread to surrounding countries 
also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
and Syria.

These mass movements would not have been possible without
efficient large-scale coordination, both physically and virtually on social
media platforms. Along with Facebook, Twitter has been credited as essential 
to the Arab Spring---both for protesters (as a means to coordinate with one 
another and to communicate with the world) and for the government response
(to monitor and track protestors to crack down on dissent) [@comninos2011twitter]. 
The events of Arab Spring have been
thoroughly discussed within the political science literature
[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
the direct coupling between Syrian Twitter use and international action
has not been investigated.
